---
title: "Survey Progress Report"
author: "Real-time Analytics"
date: "`r format(Sys.time(), '%d-%m-%Y %H:%M:%S')`"
output:
    html_document:
        theme: readable
params:
    username: '$$FilterValue::get_user_info("##USERNAME##","username")$$'
    userrole: '$$FilterValue::get_user_info(FilterValue::get_user_info("##USERNAME##","username"), "user_role")$$'
    fullname: '$$FilterValue::get_user_info(FilterValue::get_user_info("##USERNAME##","username"), "fullname")$$'
    projcode: '$$FilterValue::get_my_projectcode()$$'
---


<style>
    body .main-container {
        max-width: 100%;
    }
</style>

<style type="text/css">

body{ /* Normal  */
      font-size: 14px;
  }
td {  /* Table  */
  font-size: 15px;
}
h1.title {
  font-size: 30px;
  color: DarkRed;
}

h1 { /* Header 1 */
  font-size: 30px;
  <!-- color: DarkBlue; -->
}
h2 { /* Header 2*/
    font-size: 25px;
  <!-- color: DarkBlue; -->
}
h3 { /* Header 3 */
  font-size: 20px;
  font-family: "Times New Roman", Times, serif;
  <!-- color: DarkBlue; -->
}
code.r{ /* Code block */
    font-size: 14px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 15px;
}
</style>


```{r setup, include=FALSE}

## -----------------------------------------------------------------------------
## global setup

knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE, warning = FALSE)
options(shiny.sanitize.errors = FALSE, scipen = 999)
options(knitr.kable.NA = '')
Sys.setlocale(category = "LC_ALL", locale = "en_US.UTF-8")

## -----------------------------------------------------------------------------
## load packages

RTA::load_packages(readr, tidyr, knitr, dplyr, RTA, highcharter)

## -----------------------------------------------------------------------------
## import data
import_family_data(site = params$projcode)
import_uploaded_data(site = params$projcode)
report <- "~/gambia/analytics/reports/rmarkdown/2018-04-12_survey_progress.Rmd"

```


```{r helper-function, include=FALSE}
	
choice_dict <- function(data, var) {
    out <- data %>% 
        filter(list_name == var) %>% 
        filter(!duplicated(name_id)) 
    out <- make_dict(out$name_id,
                     out$name_lb)
}	
	
theme <- hc_theme(
  chart = list(
    plotBorderColor = '#606063',
            style = list(
              fontFamily = "Roboto",
              color = '#3C3C3C'
            )
  ),
  title = list(
    align = "left",
    x = 70,
    style = list(
      fontWeight = "bold"
    )
  ),
  subtitle = list(
    align = "left",
    x = 70
  )
)

plot_progress_by_day <- function(df) {
    df <- count(df, date)
    hchart(df, "column",
           hcaes(date, n),
           color = "#228B22",
           name = "Instance") %>%
    # hc_legend(enabled = FALSE) %>%
        hc_xAxis(categories = as.list(df$date),
                 title = list(enabled = FALSE)) %>% 
        hc_yAxis(title = list(text = "Number of instances per day",
                              style = list(fontSize = "15px")),
                 align = "left",
                 showFirstLabel = FALSE,
                 showLastLabel = FALSE) %>%
        hc_title(text = paste("Total interviews conducted:", sum(df$n))) %>%
        # hc_subtitle(text = paste("Updated:",
        #                          paste0(df$date[nrow(df)]))) %>%
        hc_subtitle(text = paste0("Total Success: ", nrow(gambia[gambia$consent == "Success", ]), " - ",
                                  "Total Failed: ", nrow(gambia[gambia$consent == "Fail", ]), " - ",
                                  "Total Refuse: ", nrow(gambia[gambia$consent == "Refuse", ]))) %>% 
        hc_credits(enabled = TRUE,
                   text = "www.rta.vn",
                   href = "http://www.rta.vn/",
                   style = list(color = "darkgreen",
                                fontFize = "15px")) %>%
        hc_add_theme(theme) %>%
        hc_exporting(enabled = TRUE) %>% 
        hc_plotOptions(series = list(stacking = "normal"))
}

plot_interview_time <- function(df) {
    hchart(df$duration) %>%
        hc_legend(enabled = FALSE) %>%
        hc_title(text = "Distribution of interview time") %>%
        hc_xAxis(title = list(text = "Interview duration (unit: mins)")) %>%
        hc_yAxis(title = list(text = "Number of instances")) %>%
        hc_credits(enabled = TRUE,
                   text = "www.rta.vn",
                   href = "http://www.rta.vn/",
                   style = list(color = "darkgreen",
                                fontFize = "15px")) %>%
        hc_add_theme(theme) %>%
        hc_exporting(enabled = TRUE)
}

plot_progress_by_var <- function(df, var, name_title, types = "bar", colors = "#228B22") {
    if(nrow(df) > 0) {
        df <- count(df, new = df[[var]])
	  	df <- filter(df, !is.na(new))
        df <- arrange(df, desc(n))
        hchart(df, type = types, hcaes(new, n), 
			   color = colors, name = "Instance") %>%
            hc_legend(enabled = FALSE) %>%
            hc_xAxis(categories = as.list(df$new),
                     title = list(enabled = FALSE)) %>%
            hc_yAxis(title = list(text = "Number of instances",
                                  style = list(fontSize = "15px")),
                     align = "left",
                     showFirstLabel = FALSE,
                     showLastLabel = FALSE) %>%
            hc_title(text = "") %>%
            hc_credits(enabled = TRUE,
                       text = "www.rta.vn",
                       href = "http://www.rta.vn/",
                       style = list(color = "darkgreen",
                                    fontFize = "15px")) %>%
            # hc_add_series(name = "Instance",
            #              data = df$n,
            #              color = colors,
            #              type = types) %>%
            hc_add_theme(theme) %>%
            hc_exporting(enabled = TRUE)
        # if (nrow(df) < 90) {
        #     h <- h %>% 
        #         hc_xAxis()
        # }
        
    }
    
}

table_per_var_and_date <- function(df, var) {
    
    
    if (nrow(df) > 0) {
        df <- df %>% 
            count(new = df[[var]], date) %>% 
            spread(new, n) %>% 
            mutate(Total =  apply(.[, -c(1)], 1, sum, na.rm = TRUE))
        df_rowsum <- df %>%
            summarise_at(names(.)[names(.) != c("date")], sum, na.rm = TRUE) %>%
            mutate(date = "<font color='#298A08'><b>Total</b></font>")
        df <- bind_rows(df, df_rowsum)
        names(df) <- capwords(names(df))
        kable(df)
    } else cat("<font color='red'><b>There isn't any data at this moment</b></font><br>")
    
}

```


```{r tranform-data, include=FALSE}


## -----------------------------------------------------------------------------
## combine data
gambia_hh <- bind_rows(gambia_hh, gambia_hh_ab)

## -----------------------------------------------------------------------------
## NAME DICT

col <- c("username", "fullname", "family_id", 
         "submission_date", "starttime", "endtime",
         "instanceID", "instanceName" ,"deviceid", "consent")

col_f1 <- c("f1_region_id", "f1_region_lb",
            "f1_hf_id", "f1_hf_lb", 
            "f1_result", "f1_result_other", "f1_tranlator",
            "f1_lang", "f1_lang_other")
col_name_f1 <- c("region_id", "region_lb", 
                 "facility", "facility_lb",
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")

col_f2 <- c("f2_region", "f2_region_lb", 
            "f2_faci", "f2_faci_lb",
            "f2_control_3", "f2_control_3_other", 
            "f2_control_4", "f2_control_5",
            "f2_control_5_other")
col_name_f2 <- c("region_id", "region_lb", 
                 "facility", "facility_lb",
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")


col_f3 <- c("f3_region", "f3_region_lb", 
            "f3_h_facility", "f3_h_facility_lb", 
            "f3_control_3",
            "f3_control_3_other", "f3_control_4", "f3_control_5",
            "f3_control_5_other")
col_name_f3 <- c("region_id", "region_lb",  
                 "facility", 
                 "facility_lb", 
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")

col_f4 <- c("f4_region", "f4_region_lb", 
            "f4_h_facility",
            "f4_h_facility_lb", 
            "f4_control_3",
            "f4_control_3_other", "f4_control_4", "f4_control_5",
            "f4_control_5_other")
col_name_f4 <- c("region_id", "region_lb",
                 "facility", 
                 "facility_lb", 
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")

col_hh <- c("fh_region", "fh_region_lb", "fh_eacode", "fh_eacode_lb",
            "fh_control_2", "fh_control_2_other",
            "fh_control_3", "fh_control_4",
            "fh_control_4_other")
col_name_hh <- c("region_id", "region_lb", "eacode", "eacode_lb",
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")

col_vdc <- c("vdc_region", "vdc_region_lb", 
             "vdc_control_3", "vdc_control_3_other", 
             "vdc_control_4", "vdc_control_5",
             "vdc_control_5_other")
col_name_vdc <- c("region_id", "region_lb", 
                  "result", "result_other", "tranlator",
                  "lang", "lang_other")

col_vsg <- c("vsg_region", "vsg_region_lb", 
             "vsg_control_3",
             "vsg_control_3_other", "vsg_control_4", "vsg_control_5",
             "vsg_control_5_other")

col_name_vsg <- c("region_id", "region_lb", 
                  "result", "result_other", "tranlator",
                  "lang", "lang_other")

name_dict_f1 <- make_dict(col_f1, col_name_f1)
name_dict_f2 <- make_dict(col_f2, col_name_f2)
name_dict_f3 <- make_dict(col_f3, col_name_f3)
name_dict_f4 <- make_dict(col_f4, col_name_f4)
name_dict_hh <- make_dict(col_hh, col_name_hh)
name_dict_vdc <- make_dict(col_vdc, col_name_vdc)
name_dict_vsg <- make_dict(col_vsg, col_name_vsg)

## -----------------------------------------------------------------------------
## select column

gambia_f1 <- gambia_f1 %>% 
    select(col, col_f1) %>% 
    mutate(family_id = "F1")

gambia_f2 <- gambia_f2 %>% 
    select(col, col_f2) %>% 
    mutate(family_id = "F2")

gambia_f3 <- gambia_f3 %>% 
    select(col, col_f3) %>% 
    mutate(family_id = "F3")

gambia_f4 <- gambia_f4 %>% 
    select(col, col_f4) %>% 
    mutate(family_id = "F4")

gambia_hh <- gambia_hh %>% 
    select(col, col_hh) %>% 
    mutate(family_id = "HH")

gambia_vdc <- gambia_vdc %>% 
    select(col, col_vdc) %>% 
    mutate(family_id = "VDC")

gambia_vsg <- gambia_vsg %>% 
    select(col, col_vsg) %>% 
    mutate(family_id = "VSG")


## -----------------------------------------------------------------------------
## change name
names(gambia_f1) <- encode(names(gambia_f1), name_dict_f1)
names(gambia_f2) <- encode(names(gambia_f2), name_dict_f2)
names(gambia_f3) <- encode(names(gambia_f3), name_dict_f3)
names(gambia_f4) <- encode(names(gambia_f4), name_dict_f4)
names(gambia_hh) <- encode(names(gambia_hh), name_dict_hh)
names(gambia_vdc) <- encode(names(gambia_vdc), name_dict_vdc)
names(gambia_vsg) <- encode(names(gambia_vsg), name_dict_vsg)

## -----------------------------------------------------------------------------
## combine data
gambia <- bind_rows(gambia_f1, gambia_f2, gambia_f3, gambia_f4,
                    gambia_hh, gambia_vdc, gambia_vsg)


## -----------------------------------------------------------------------------
## deal with instance

gambia <- handle_edited_insts(gambia, "instanceID")
gambia <- handle_followed_insts(gambia, "instanceID")
gambia <- handle_returned_insts(gambia, "instanceID")
gambia <- handle_revised_insts(gambia, "instanceID")


## -----------------------------------------------------------------------------
## clean data
gambia <- replace_with_na(gambia)

gambia <- mutate(gambia,
                 date = substr(submission_date, 1, 10))

## -----------------------------------------------------------------------------
## make dict
username_dict <- distinct(gambia, username, fullname)
username_dict <- make_dict(username_dict$username, username_dict$fullname)

consent_dict <- choice_dict(choice_name, "accord")
hf_type_dict <- choice_dict(choice_name, "hf_type")
result_dict <- choice_dict(choice_name, "result")
lang_dict <- choice_dict(choice_name, "language")
translator_dict <- choice_dict(choice_name, "tranlator")

family <- c("F1", "F2", "F3", "F4", 
             "HH", "VDC", "VSG")

gambia <- mutate(gambia,
                 fullname = encode(fullname, username_dict),
                 consent = encode(consent, consent_dict),
                 # hf_type = encode(hf_type, hf_type_dict),
                 result = encode(result, result_dict),
                 lang = encode(lang, lang_dict),
                 result = ifelse(is.na(result_other), result, 
                                 paste0(result, " ", result_other)),
                 lang = ifelse(is.na(lang_other), lang, 
                               paste0(lang, " ", lang_other)),
                 tranlator = encode(tranlator, translator_dict))

## -----------------------------------------------------------------------------
## calculate duration

gambia <- mutate(gambia,
                 starttime = ifelse(is.na(starttime) | starttime == "", submission_date, starttime),
                 endtime = ifelse(is.na(endtime) | endtime == "", submission_date, endtime),
                 duration = round(difftime(strptime(endtime, format = "%Y-%m-%d %H:%M:%S"),
                                           strptime(starttime, format = "%Y-%m-%d %H:%M:%S"), 
                                           units = "mins"), 2),
                 duration = ifelse(duration < 0, 0, duration))

## deal with duration time is too long
## outlier <- boxplot(gambia$duration, range = 3)$out
## max_duration <- max(gambia$duration[!gambia$duration %in% outlier])
## gambia$duration[gambia$duration > max_duration] <- max_duration

## quantitle
if (length(unique(gambia$duration)) == 1) {
    gambia$qtime <- gambia$duration
} else {
    gambia$qtime <- cut(gambia$duration, 
                        unique(quantile(gambia$duration)), include.lowest = T)
}


F1 <- filter(gambia, family_id == "F1")
F2 <- filter(gambia, family_id == "F2")
F3 <- filter(gambia, family_id == "F3")
F4 <- filter(gambia, family_id == "F4")
HH <- filter(gambia, family_id == "HH")
VDC <- filter(gambia, family_id == "VDC")
VSG <- filter(gambia, family_id == "VSG")

```

```{r calculate, include=FALSE}


## -----------------------------------------------------------------------------
### Aggregate by date
sum_per_date <- gambia %>% 
    count(date, family_id) %>% 
    spread(family_id, n) %>% 
    arrange(desc(date)) %>% 
    mutate(Total = apply(.[, -c(1)], 1, sum, na.rm = TRUE))

sum_per_date_rowsum <- sum_per_date %>% 
    summarise_at(names(.)[names(.) != c("date")], sum, na.rm = TRUE) %>% 
    mutate(date = "<font color='#298A08'><b>Total</b></font>")

sum_per_date <- bind_rows(sum_per_date, sum_per_date_rowsum)
names(sum_per_date) <- capwords(names(sum_per_date))

## -----------------------------------------------------------------------------
## count by qtime
detail <- gambia %>% 
    count(family_id, date, fullname, qtime) %>% 
    spread(qtime, n) %>% 
    mutate(Total = apply(.[, -c(1:3)], 1, sum, na.rm = TRUE))

detail <- arrange(detail, desc(date, Total))
names(detail) <- capwords(names(detail))

```


## 1. Total Interview {.tabset}

### Summary

```{r ui}

plot_progress_by_day(gambia)

```

### Detail

```{r, results='asis'}


kable(sum_per_date)

```

## 2. Total interviews conducted by status{.tabset}

### Summary

```{r, results='asis'}

plot_progress_by_var(df = gambia, 
                     var = "consent", 
                     type = "column",
                     name_title = "Distribution of instances by status")

```

### Detail {.tabset}


#### F1

```{r, results='asis'}

table_per_var_and_date(F1, "consent")

```


#### F2

```{r, results='asis'}

table_per_var_and_date(F2, "consent")

```

#### F3

```{r, results='asis'}

table_per_var_and_date(F3, "consent")

```

#### F4

```{r, results='asis'}

table_per_var_and_date(F4, "consent")

```

#### HH

```{r, results='asis'}

table_per_var_and_date(HH, "consent")

```

#### VDC

```{r, results='asis'}

table_per_var_and_date(VDC, "consent")

```

#### VSG

```{r, results='asis'}

table_per_var_and_date(VSG, "consent")

```



## 3. Total interviews conducted by region{.tabset}

### Summary

```{r, results='asis'}

plot_progress_by_var(df = gambia, 
                     var = "region_lb", 
                     name_title = "Distribution of instances by region")

```

### Detail {.tabset}

#### F1

```{r, results='asis'}

table_per_var_and_date(F1, "region_lb")

```


#### F2

```{r, results='asis'}

table_per_var_and_date(F2, "region_lb")

```

#### F3

```{r, results='asis'}

table_per_var_and_date(F3, "region_lb")

```

#### F4

```{r, results='asis'}

table_per_var_and_date(F4, "region_lb")

```

#### HH

```{r, results='asis'}

table_per_var_and_date(HH, "region_lb")

```

#### VDC

```{r, results='asis'}

table_per_var_and_date(VDC, "region_lb")

```

#### VSG

```{r, results='asis'}

table_per_var_and_date(VSG, "region_lb")

```



## 4. Total interviews conducted by enum{.tabset}

### Summary

```{r, results='asis'}

plot_progress_by_var(df = gambia, 
                     var = "fullname", 
                     name_title = "Distribution of instances by enum")

plot_interview_time(gambia)




```

### Detail {.tabset}

*Unit: mins*

#### F1

```{r, results='asis'}

f1 <- detail %>% filter(Family_id == "F1") %>% select(-Family_id)
if (nrow(f1) > 0) {
    kable(f1)
} else cat("<font color='red'><b>There isn't any data at this moment</b></font><br>")


```


#### F2

```{r, results='asis'}

f2 <- detail %>% filter(Family_id == "F2") %>% select(-Family_id)
if (nrow(f2) > 0) {
    kable(f2)
} else cat("<font color='red'><b>There isn't any data at this moment</b></font><br>")


```

#### F3

```{r, results='asis'}

f3 <- detail %>% filter(Family_id == "F3") %>% select(-Family_id)
if (nrow(f3) > 0) {
    kable(f3)
} else cat("<font color='red'><b>There isn't any data at this moment</b></font><br>")


```

#### F4

```{r, results='asis'}

f4 <- detail %>% filter(Family_id == "F4") %>% select(-Family_id)
if (nrow(f4) > 0) {
    kable(f4)
} else cat("<font color='red'><b>There isn't any data at this moment</b></font><br>")


```

#### HH

```{r, results='asis'}

hh <- detail %>% filter(Family_id == "HH") %>% select(-Family_id)
if (nrow(hh) > 0) {
    kable(hh)
} else cat("<font color='red'><b>There isn't any data at this moment</b></font><br>")


```

#### VDC

```{r, results='asis'}

vdc <- detail %>% filter(Family_id == "VDC") %>% select(-Family_id)
if (nrow(vdc) > 0) {
    kable(vdc)
} else cat("<font color='red'><b>There isn't any data at this moment</b></font><br>")


```

#### VSG

```{r, results='asis'}

vsg <- detail %>% filter(Family_id == "VSG") %>% select(-Family_id)
if (nrow(vsg) > 0) {
    kable(vsg)
} else cat("<font color='red'><b>There isn't any data at this moment</b></font><br>")


```

