---
title: "QA Report"
author: "Real-time Analytics"
date: "`r format(Sys.time(), '%d-%m-%Y %H:%M:%S')`"
output:
    html_document:
        theme: readable
params:
    username: '$$FilterValue::get_user_info("##USERNAME##","username")$$'
    userrole: '$$FilterValue::get_user_info(FilterValue::get_user_info("##USERNAME##","username"), "user_role")$$'
    fullname: '$$FilterValue::get_user_info(FilterValue::get_user_info("##USERNAME##","username"), "fullname")$$'
    projcode: '$$FilterValue::get_my_projectcode()$$'
---

<style>
    body .main-container {
        max-width: 100%;
    }
</style>

<style type="text/css">

body{ /* Normal  */
      font-size: 13px;
  }
td {  /* Table  */
  font-size: 14px;
}
h1.title {
  font-size: 30px;
  color: DarkRed;
}
h1.author {
  font-size: 14px;
  color: DarkRed;
}
h1.date {
  font-size: 14px;
}
h1 { /* Header 1 */
  font-size: 30px;
  <!-- color: DarkBlue; -->
}
h2 { /* Header 2*/
    font-size: 25px;
  <!-- color: DarkBlue; -->
}
h3 { /* Header 3 */
  font-size: 20px;
  font-family: "Times New Roman", Times, serif;
  <!-- color: DarkBlue; -->
}
code.r{ /* Code block */
    font-size: 13px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 14px;
}
</style>


```{r setup, include=FALSE}

## -----------------------------------------------------------------------------
## global setup

knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE, warning = FALSE)
options(shiny.sanitize.errors = FALSE, scipen = 999)
Sys.setlocale(category = "LC_ALL", locale = "en_US.UTF-8")
options(knitr.kable.NA = '')

## -----------------------------------------------------------------------------
## load packages

RTA::load_packages(readr, tidyr, dplyr, knitr, RTA)

## -----------------------------------------------------------------------------
## import data

import_family_data(site = params$projcode)
import_uploaded_data(site = params$projcode)
report <- "~/gambia/analytics/reports/rmarkdown/2018-04-10_qa_report.Rmd"


```


```{r helper-function, include=FALSE}

choice_dict <- function(data, var) {
    out <- data %>% 
        filter(list_name == var) %>% 
        filter(!duplicated(name_id)) 
    out <- make_dict(out$name_id,
                     out$name_lb)
}

```

	
```{r tranform-data, include=FALSE}


## -----------------------------------------------------------------------------
## combine data
gambia_hh <- bind_rows(gambia_hh, gambia_hh_ab)

## -----------------------------------------------------------------------------
## NAME DICT

col <- c("username", "fullname", "family_id", 
         "submission_date", "starttime", "endtime",
         "instanceID", "instanceName" ,"deviceid", "consent")

col_f1 <- c("f1_region_id", "f1_region_lb",
            "f1_hf_id", "f1_hf_lb", 
            "f1_result", "f1_result_other", "f1_tranlator",
            "f1_lang", "f1_lang_other")
col_name_f1 <- c("region_id", "region_lb", 
                 "facility", "facility_lb",
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")

col_f2 <- c("f2_region", "f2_region_lb", 
            "f2_faci", "f2_faci_lb",
            "f2_control_3", "f2_control_3_other", 
            "f2_control_4", "f2_control_5",
            "f2_control_5_other")
col_name_f2 <- c("region_id", "region_lb", 
                 "facility", "facility_lb",
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")


col_f3 <- c("f3_region", "f3_region_lb", 
            "f3_h_facility", "f3_h_facility_lb", 
            "f3_control_3",
            "f3_control_3_other", "f3_control_4", "f3_control_5",
            "f3_control_5_other")
col_name_f3 <- c("region_id", "region_lb",  
                 "facility", 
                 "facility_lb", 
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")

col_f4 <- c("f4_region", "f4_region_lb", 
            "f4_h_facility",
            "f4_h_facility_lb", 
            "f4_control_3",
            "f4_control_3_other", "f4_control_4", "f4_control_5",
            "f4_control_5_other")
col_name_f4 <- c("region_id", "region_lb",
                 "facility", 
                 "facility_lb", 
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")

col_hh <- c("fh_region", "fh_region_lb", "fh_eacode", "fh_eacode_lb",
            "fh_control_2", "fh_control_2_other",
            "fh_control_3", "fh_control_4",
            "fh_control_4_other")
col_name_hh <- c("region_id", "region_lb", "eacode", "eacode_lb",
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")

col_vdc <- c("vdc_region", "vdc_region_lb", 
             "vdc_control_3", "vdc_control_3_other", 
             "vdc_control_4", "vdc_control_5",
             "vdc_control_5_other")
col_name_vdc <- c("region_id", "region_lb", 
                  "result", "result_other", "tranlator",
                  "lang", "lang_other")

col_vsg <- c("vsg_region", "vsg_region_lb", 
             "vsg_control_3",
             "vsg_control_3_other", "vsg_control_4", "vsg_control_5",
             "vsg_control_5_other")

col_name_vsg <- c("region_id", "region_lb", 
                  "result", "result_other", "tranlator",
                  "lang", "lang_other")

name_dict_f1 <- make_dict(col_f1, col_name_f1)
name_dict_f2 <- make_dict(col_f2, col_name_f2)
name_dict_f3 <- make_dict(col_f3, col_name_f3)
name_dict_f4 <- make_dict(col_f4, col_name_f4)
name_dict_hh <- make_dict(col_hh, col_name_hh)
name_dict_vdc <- make_dict(col_vdc, col_name_vdc)
name_dict_vsg <- make_dict(col_vsg, col_name_vsg)

## -----------------------------------------------------------------------------
## select column

gambia_f1 <- gambia_f1 %>% 
    select(col, col_f1) %>% 
    mutate(family_id = "F1")

gambia_f2 <- gambia_f2 %>% 
    select(col, col_f2) %>% 
    mutate(family_id = "F2")

gambia_f3 <- gambia_f3 %>% 
    select(col, col_f3) %>% 
    mutate(family_id = "F3")

gambia_f4 <- gambia_f4 %>% 
    select(col, col_f4) %>% 
    mutate(family_id = "F4")

gambia_hh <- gambia_hh %>% 
    select(col, col_hh) %>% 
    mutate(family_id = "HH")

gambia_vdc <- gambia_vdc %>% 
    select(col, col_vdc) %>% 
    mutate(family_id = "VDC")

gambia_vsg <- gambia_vsg %>% 
    select(col, col_vsg) %>% 
    mutate(family_id = "VSG")

## -----------------------------------------------------------------------------
## change name
names(gambia_f1) <- encode(names(gambia_f1), name_dict_f1)
names(gambia_f2) <- encode(names(gambia_f2), name_dict_f2)
names(gambia_f3) <- encode(names(gambia_f3), name_dict_f3)
names(gambia_f4) <- encode(names(gambia_f4), name_dict_f4)
names(gambia_hh) <- encode(names(gambia_hh), name_dict_hh)
names(gambia_vdc) <- encode(names(gambia_vdc), name_dict_vdc)
names(gambia_vsg) <- encode(names(gambia_vsg), name_dict_vsg)


## -----------------------------------------------------------------------------
## combine data
gambia <- bind_rows(gambia_f1, gambia_f2, gambia_f3, gambia_f4,
                    gambia_hh, gambia_vdc, gambia_vsg)

## -----------------------------------------------------------------------------
## clean data
gambia <- replace_with_na(gambia)

gambia <- mutate(gambia,
                 date = substr(submission_date, 1, 10))

## make dict
username_dict <- distinct(gambia, username, fullname)
username_dict <- make_dict(username_dict$username, username_dict$fullname)

consent_dict <- choice_dict(choice_name, "accord")
hf_type_dict <- choice_dict(choice_name, "hf_type")
result_dict <- choice_dict(choice_name, "result")
lang_dict <- choice_dict(choice_name, "language")
translator_dict <- choice_dict(choice_name, "tranlator")

family <- c("F1", "F2", "F3", "F4", 
             "HH", "VDC", "VSG")

gambia <- mutate(gambia,
                 fullname = encode(fullname, username_dict),
                 consent = encode(consent, consent_dict),
                 # hf_type = encode(hf_type, hf_type_dict),
                 result = encode(result, result_dict),
                 lang = encode(lang, lang_dict),
                 result = ifelse(is.na(result_other), result, 
                                 paste0(result, " ", result_other)),
                 lang = ifelse(is.na(lang_other), lang, 
                               paste0(lang, " ", lang_other)),
                 tranlator = encode(tranlator, translator_dict))


## -----------------------------------------------------------------------------
## calculate duration

gambia <- mutate(gambia,
                 # starttime = substr(starttime, 12, 19),
                 # endtime = substr(endtime, 12, 19),
                 duration = round(difftime(strptime(endtime, format = "%Y-%m-%d %H:%M:%S"),
                                     strptime(starttime, format = "%Y-%m-%d %H:%M:%S"), 
                                     units = "mins"), 2),
                 duration = as.double(duration))

## -----------------------------------------------------------------------------
## deal with duration time is too long

outlier <- boxplot(gambia$duration, range = 3)$out
max_duration <- max(gambia$duration[!gambia$duration %in% outlier])
min_duration <- min(gambia$duration[!gambia$duration %in% outlier])
gambia_time_long <- filter(gambia, duration > max_duration)
gambia_time_short <- filter(gambia, duration < min_duration)
gambia_time <- bind_rows(gambia_time_long, gambia_time_short)
gambia_time <- select(gambia_time, 
                      fullname, instanceID, deviceid, 
                      submission_date, starttime, endtime, duration)
names(gambia_time) <- capwords(names(gambia_time))

## -----------------------------------------------------------------------------
## deal with instance

gambia$instanceID_new <- substr(gambia$instanceID, 1, 41)
duplicated_instance <- filter(gambia, duplicated(gambia$instanceID_new)) %>% 
    select(instanceID_new) %>% unlist()
gambia_dup <- filter(gambia, instanceID_new %in% duplicated_instance) %>% 
    select(fullname, instanceID, region_id, region_lb, submission_date, deviceid)

names(gambia_dup) <- capwords(names(gambia_dup))

## -----------------------------------------------------------------------------
## deal with time

start_na <- filter(gambia, is.na(starttime) | grepl("^1970", starttime))
end_na <- filter(gambia, is.na(endtime)| grepl("^1970", endtime))
sub_na <- filter(gambia, is.na(submission_date)| grepl("^1970", submission_date))
time_na <- bind_rows(start_na, end_na, sub_na)
time_na <- select(time_na,
                  fullname, instanceID, instanceName, deviceid, 
                  submission_date, starttime, endtime)
names(time_na) <- capwords(names(time_na))


## -----------------------------------------------------------------------------
## deal with miss some column

miss_data <- filter(gambia, is.na(region_lb) | is.na(username)) %>% 
    select(fullname, 
		   instanceID, deviceid, submission_date, region_id, region_lb, username)
names(miss_data) <- capwords(names(miss_data))


```


```{r, results='asis'}



cat("<br>")
cat("<br>")  
  
```

### **1. Returned Instance, Edited Instance, Followed Instance, Revised Instance**

```{r instance, results='asis'}

if (nrow(gambia_dup) > 0) {
    kable(gambia_dup)
} else cat("<font color='red'><b>The data does not have modified instance</b></font><br>")

cat("<br>")
cat("<br>")  
  
```

### **2. Missing region_lb, username**

```{r, results='asis'}

if (nrow(miss_data) > 0) {
    kable(miss_data)
} else cat("<font color='red'><b>The data does not miss these values</b></font><br>")

cat("<br>")
cat("<br>")  

```



### **3. Time**

#### a. Missing submission_date, starttime, endtime or starttime, endtime start with "1970-01-01"

```{r missing-time, results='asis'}

if (nrow(time_na) > 0) {
    kable(time_na)
} else cat("<font color='red'><b>The data does not miss these values</b></font><br>")

cat("<br>")
  
```

#### b. Duration too long or too short (unit: mins)

```{r duration, results='asis'}

if (nrow(gambia_time) > 0) {
    kable(gambia_time)
} else cat("<font color='red'><b>There isn't any data in this case</b></font><br>")


```

