---
title: "Survey Progress By Enum"
author: "Real-time Analytics"
date: "`r format(Sys.time(), '%d-%m-%Y %H:%M:%S')`"
output:
    html_document:
        theme: readable
params:
    username: '$$FilterValue::get_user_info("##USERNAME##","username")$$'
    userrole: '$$FilterValue::get_user_info(FilterValue::get_user_info("##USERNAME##","username"), "user_role")$$'
    fullname: '$$FilterValue::get_user_info(FilterValue::get_user_info("##USERNAME##","username"), "fullname")$$'
    projcode: '$$FilterValue::get_my_projectcode()$$'      

---

<style>
    body .main-container {
        max-width: 100%;
    }
</style>

<style type="text/css">

body{ /* Normal  */
      font-size: 14px;
  }
td {  /* Table  */
  font-size: 15px;
}
h1.title {
  font-size: 30px;
  color: DarkRed;
}
h1.author {
  font-size: 15px;
  color: DarkRed;
}
h1.date {
  font-size: 15px;
}
h1 { /* Header 1 */
  font-size: 30px;
  <!-- color: DarkBlue; -->
}
h2 { /* Header 2*/
    font-size: 25px;
  <!-- color: DarkBlue; -->
}
h3 { /* Header 3 */
  font-size: 20px;
  font-family: "Times New Roman", Times, serif;
  <!-- color: DarkBlue; -->
}
code.r{ /* Code block */
    font-size: 14px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 15px;
}
</style>


```{r setup, include=FALSE}

## -----------------------------------------------------------------------------
## global setup

knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE, warning = FALSE)
options(shiny.sanitize.errors = FALSE, scipen = 999)
options(knitr.kable.NA = '')
Sys.setlocale(category = "LC_ALL", locale = "en_US.UTF-8")

## -----------------------------------------------------------------------------
## load packages

RTA::load_packages(readr, tidyr, dplyr, DT, knitr, RTA)

## -----------------------------------------------------------------------------
## import data

# auto_import_all(site = params$projcode)
import_family_data(site = params$projcode)
import_uploaded_data(site = params$projcode)
report <- "~/gambia/analytics/reports/rmarkdown/2018-04-09_survey-progress-by-enum.Rmd"


```

```{r helper-function, include=FALSE}

choice_dict <- function(data, var) {
    out <- data %>% 
        filter(list_name == var) %>% 
        filter(!duplicated(name_id)) 
    out <- make_dict(out$name_id,
                     out$name_lb)
}

```


```{r tranform-data, include=FALSE}

## -----------------------------------------------------------------------------
## combine data
gambia_hh <- bind_rows(gambia_hh, gambia_hh_ab)

## -----------------------------------------------------------------------------
## NAME DICT

col <- c("username", "fullname", "family_id", 
         "submission_date", "starttime", "endtime",
         "instanceID", "instanceName" ,"deviceid", "consent")

col_f1 <- c("f1_region_id", "f1_region_lb",
            "f1_hf_id", "f1_hf_lb", 
            "f1_result", "f1_result_other", "f1_tranlator",
            "f1_lang", "f1_lang_other")
col_name_f1 <- c("region_id", "region_lb", 
                 "facility", "facility_lb",
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")

col_f2 <- c("f2_region", "f2_region_lb", 
            "f2_faci", "f2_faci_lb",
            "f2_control_3", "f2_control_3_other", 
            "f2_control_4", "f2_control_5",
            "f2_control_5_other")
col_name_f2 <- c("region_id", "region_lb", 
                 "facility", "facility_lb",
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")


col_f3 <- c("f3_region", "f3_region_lb", 
            "f3_h_facility", "f3_h_facility_lb", 
            "f3_control_3",
            "f3_control_3_other", "f3_control_4", "f3_control_5",
            "f3_control_5_other")
col_name_f3 <- c("region_id", "region_lb",  
                 "facility", 
                 "facility_lb", 
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")

col_f4 <- c("f4_region", "f4_region_lb", 
            "f4_h_facility",
            "f4_h_facility_lb", 
            "f4_control_3",
            "f4_control_3_other", "f4_control_4", "f4_control_5",
            "f4_control_5_other")
col_name_f4 <- c("region_id", "region_lb",
                 "facility", 
                 "facility_lb", 
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")

col_hh <- c("fh_region", "fh_region_lb", "fh_eacode", "fh_eacode_lb",
            "fh_control_2", "fh_control_2_other",
            "fh_control_3", "fh_control_4",
            "fh_control_4_other")
col_name_hh <- c("region_id", "region_lb", "eacode", "eacode_lb",
                 "result", "result_other", "tranlator",
                 "lang", "lang_other")

col_vdc <- c("vdc_region", "vdc_region_lb", 
             "vdc_control_3", "vdc_control_3_other", 
             "vdc_control_4", "vdc_control_5",
             "vdc_control_5_other")
col_name_vdc <- c("region_id", "region_lb", 
                  "result", "result_other", "tranlator",
                  "lang", "lang_other")

col_vsg <- c("vsg_region", "vsg_region_lb", 
             "vsg_control_3",
             "vsg_control_3_other", "vsg_control_4", "vsg_control_5",
             "vsg_control_5_other")

col_name_vsg <- c("region_id", "region_lb", 
                  "result", "result_other", "tranlator",
                  "lang", "lang_other")

name_dict_f1 <- make_dict(col_f1, col_name_f1)
name_dict_f2 <- make_dict(col_f2, col_name_f2)
name_dict_f3 <- make_dict(col_f3, col_name_f3)
name_dict_f4 <- make_dict(col_f4, col_name_f4)
name_dict_hh <- make_dict(col_hh, col_name_hh)
name_dict_vdc <- make_dict(col_vdc, col_name_vdc)
name_dict_vsg <- make_dict(col_vsg, col_name_vsg)

## -----------------------------------------------------------------------------
## select column

gambia_f1 <- gambia_f1 %>% 
    select(col, col_f1) %>% 
    mutate(family_id = "F1")

gambia_f2 <- gambia_f2 %>% 
    select(col, col_f2) %>% 
    mutate(family_id = "F2")

gambia_f3 <- gambia_f3 %>% 
    select(col, col_f3) %>% 
    mutate(family_id = "F3")

gambia_f4 <- gambia_f4 %>% 
    select(col, col_f4) %>% 
    mutate(family_id = "F4")

gambia_hh <- gambia_hh %>% 
    select(col, col_hh) %>% 
    mutate(family_id = "HH")

gambia_vdc <- gambia_vdc %>% 
    select(col, col_vdc) %>% 
    mutate(family_id = "VDC")

gambia_vsg <- gambia_vsg %>% 
    select(col, col_vsg) %>% 
    mutate(family_id = "VSG")

## -----------------------------------------------------------------------------
## change name
names(gambia_f1) <- encode(names(gambia_f1), name_dict_f1)
names(gambia_f2) <- encode(names(gambia_f2), name_dict_f2)
names(gambia_f3) <- encode(names(gambia_f3), name_dict_f3)
names(gambia_f4) <- encode(names(gambia_f4), name_dict_f4)
names(gambia_hh) <- encode(names(gambia_hh), name_dict_hh)
names(gambia_vdc) <- encode(names(gambia_vdc), name_dict_vdc)
names(gambia_vsg) <- encode(names(gambia_vsg), name_dict_vsg)

## -----------------------------------------------------------------------------
## combine data
gambia <- bind_rows(gambia_f1, gambia_f2, gambia_f3, gambia_f4,
                    gambia_hh, gambia_vdc, gambia_vsg)

## -----------------------------------------------------------------------------
## deal with instance

gambia <- handle_edited_insts(gambia, "instanceID")
gambia <- handle_followed_insts(gambia, "instanceID")
gambia <- handle_returned_insts(gambia, "instanceID")
gambia <- handle_revised_insts(gambia, "instanceID")


## -----------------------------------------------------------------------------
## clean data
gambia <- replace_with_na(gambia)

gambia <- mutate(gambia,
                 date = substr(submission_date, 1, 10))

## -----------------------------------------------------------------------------
## make dict
username_dict <- distinct(gambia, username, fullname)
username_dict <- make_dict(username_dict$username, username_dict$fullname)

consent_dict <- choice_dict(choice_name, "accord")
hf_type_dict <- choice_dict(choice_name, "hf_type")
result_dict <- choice_dict(choice_name, "result")
lang_dict <- choice_dict(choice_name, "language")
translator_dict <- choice_dict(choice_name, "tranlator")


family <- c("F1", "F2", "F3", "F4", 
             "HH", "VDC", "VSG")


gambia <- mutate(gambia,
                 fullname = encode(fullname, username_dict),
                 consent = encode(consent, consent_dict),
                 # hf_type = encode(hf_type, hf_type_dict),
                 result = encode(result, result_dict),
                 lang = encode(lang, lang_dict),
                 result = ifelse(is.na(result_other), result, 
                                 paste0(result, " ", result_other)),
                 lang = ifelse(is.na(lang_other), lang, 
                               paste0(lang, " ", lang_other)),
                 tranlator = encode(tranlator, translator_dict))


## -----------------------------------------------------------------------------
## calculate duration

gambia <- mutate(gambia,
                 starttime = ifelse(is.na(starttime) | starttime == "", submission_date, starttime),
                 endtime = ifelse(is.na(endtime) | endtime == "", submission_date, endtime),
                 duration = round(difftime(strptime(endtime, format = "%Y-%m-%d %H:%M:%S"),
                                           strptime(starttime, format = "%Y-%m-%d %H:%M:%S"), 
                                           units = "mins"), 2),
                 duration = ifelse(duration < 0, 0, duration))


## -----------------------------------------------------------------------------
## Filter by username

if (Sys.info()["user"] != "phuongha") {
  	user_name <- params$username
    gambia <- filter(gambia, username == user_name)
    username_dict <- distinct(gambia, username, fullname)
    
  	if (nrow(username_dict) > 0) {
        username_dict <- make_dict(username_dict$username, username_dict$fullname)
    }
}

```



```{r calculate-after-filter, include=FALSE}

if (nrow(gambia) > 0) {
    ## -----------------------------------------------------------------------------
    ## Aggregate by date and consent
    
    ## count by date, consent, fullnanme
    sum_per_date_consent <- gambia %>% 
        count(fullname, date, family_id, consent) %>% 
        spread(family_id, n) %>% 
        arrange(desc(date), fullname, consent) %>% 
        mutate(Total = apply(.[, -c(1:3)], 1, sum, na.rm = TRUE))
    
    ## Add column missing
    for (i in 1: length(family)) {
        if (!family[i] %in% names(sum_per_date_consent)) {
            sum_per_date_consent <- mutate(sum_per_date_consent,
                                           new = double(nrow(sum_per_date_consent)))
            names(sum_per_date_consent)[names(sum_per_date_consent) == "new"] <- family[i]
        }
    }
    
    ## sum per date and name
    sum_per_date_name <- sum_per_date_consent %>%
        group_by(date, fullname) %>%
        summarise_at(vars(F1, F2, F3, F4, HH, VDC, VSG, Total), funs(sum(., na.rm = TRUE))) %>%
        mutate(fullname = fullname,
               # date = date,
               consent = "<font color='#298A08'><b>Total</b></font>") %>% 
        bind_rows(sum_per_date_consent) %>%
        arrange(desc(date), fullname, desc(consent)) %>% 
        select(date, consent, everything()) %>% 
        ungroup()
    sum_per_date_name <- replace_with_na(sum_per_date_name, 0) 
    names(sum_per_date_name) <- capwords(names(sum_per_date_name))
    
    ## -----------------------------------------------------------------------------
    ## Detail
    
    detail <- select(gambia,
                     fullname, date, family_id, starttime, endtime, duration,
                     consent, region_lb)
    detail <- arrange(detail, desc(date), fullname)
    
    result_name_dict <- make_dict(c("region_lb",  
                                    "lang", "hf_type", 
                                    "facility_lb"),
                                  c("Region",  
                                    "Language", "Type", 
                                    "Facility"))
    names(detail) <- encode(names(detail), result_name_dict)
    names(detail) <- capwords(names(detail))

} else {
    sum_per_date_name <- data.frame()
    detail <- data.frame()
}

```


# {.tabset}

## **Summary**

```{r, results='asis'}

cat("<font size='3' color='#B4045F'><b>Total Interview: ", nrow(gambia), "</b></font><br>")
cat("<font size='2' color='#298A08'><b>Total Success: ", nrow(gambia[gambia$consent == "Success", ]), "</b></font><br>")
cat("<font size='2' color='#298A08'><b>Total Failed: ", nrow(gambia[gambia$consent == "Fail", ]), "</b></font><br>")
cat("<font size='2' color='#298A08'><b>Total Refuse: ", nrow(gambia[gambia$consent == "Refuse", ]), "</b></font><br>")
cat("<br>")

if (nrow(sum_per_date_name) > 0) {
    for (i in 1:length(username_dict)) {
        sum_per_date_name_i <- filter(sum_per_date_name, Fullname == username_dict[i])
        sum_per_date_name_i <- select(sum_per_date_name_i, - Fullname)
        sum_per_date_name_i_rowsum <- sum_per_date_name_i %>% 
                filter(Consent != "<font color='#298A08'><b>Total</b></font>") %>% 
                summarise_at(names(.)[names(.) != c("Date", "Consent")], sum, na.rm = TRUE) %>% 
                mutate(Date = "<font color='#B4045F'><b>Total</b></font>")
        sum_per_date_name_i <- bind_rows(sum_per_date_name_i, sum_per_date_name_i_rowsum)
        sum_per_date_name_i <- replace_with_na(sum_per_date_name_i, 0)
        cat("<font size='3' color='#B4045F'><b>", username_dict[i], "</font></b>")
        # print(kable(sum_per_date_i))
        #     cat("\n")
        print(kable(sum_per_date_name_i))
        cat("\n")
        
    }
} else cat("<font color='red'><b><div align='center'>Chưa có dữ liệu</div></b></font>")

```
  
End  

## **Detail**

```{r detail, results='asis'}

# cat("<font color='#B4045F'><b>Total Interview: ", 
#     nrow(detail), "</b></font><br>")
if (nrow(detail) > 0) {
    for (i in 1:length(username_dict)) {
        detail_i <- filter(detail, Fullname == username_dict[i])
        detail_i <- select(detail_i, - Fullname)
        cat("<font size='3' color='#B4045F'><b>", username_dict[i], "</b></font><br>")
        for (k in 1:length(family)) {
            detail_k <- filter(detail_i, Family_id == family[k])
    	  	detail_k <- select(detail_k, - Family_id)
            cat("<font color='#298A08'><b>Total Interview from", 
                family[k], ": ", 
                nrow(detail_k), "</b></font><br>")
            if (nrow(detail_k) > 0) {
                print(kable(detail_k))
                cat("\n")
            } else {
			  
			  cat("<font color='red'><b><div align='center'>Chưa có dữ liệu</div></b></font>")
			  cat("<br>")
			}
            
        }
    }
} else cat("<font color='red'><b><div align='center'>Chưa có dữ liệu</div></b></font>")
#kable(detail)

```

End
